---
title: "simp_lin_R-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(HW1Mantautas)
```


It is often useful to use a linear regression command that is very quick and very simple. Using such a function might save you a lot of time doing a parallelized simulation study related to simple regression.

This vignette would introduce how to use `sim_lin_R()` function and reach its output.

We will start by covering what inputs this function expects. 

## Basic usage

`simp_lin_R()` has two arguments:

* The first argument, `y` inputs the response variable of your choice. It must be a numeric vector of length more than 2. 

* The second argument, `x` inputs the predictor variable of your choice. The input must be a numeric vector of length more than 2 and length must be equal to `y`.

Here are a couple of examples of `sim_lin_R()` usage.

```{r, eval=FALSE}
predictor=rnorm(100)
response=rnorm(100)
simp_lin_R(y=response, x=predictor)
```

```{r, eval=FALSE}
variable1=seq(0,100,length=50)
variable2=seq(100,60, length=50)
simp_lin_R(variable1, variable2)
```

## Output

`sim_lin_R()` gives a list consisting of elements:

* `$Coefficients` gives a vector of 2 elements, where the first element consists estimated coefficient of the intercept $\hat{\beta_0}$ and the second element consists estimated coefficient of the slope $\hat{\beta_1}$.

* `$Fitted` gives vector of length equal to input vector $x$. It is calculated as $\hat{y}=\hat{\beta_0}+\hat{\beta_1}x$

* `$MSE` gives a scalar value of calculated mean squared error.

* `$Standard_Error` give a vector of 2 elements, where the first is estimated standard error of the intercept and the second is estimated standard error of the slope.

* `$Residuals` gives vector of length equal to input vector $x$. It is calculated as $e=y-\hat{y}$.

* `$95pct_conf` gives matrix of dimension 2x2. First row gives estimated $95\%$ confidence interval for $\beta_0$ and second row gives estimated $95\%$ confidence interval for $\beta_1$.

An example of the output is below.

```{r}
predictor=rnorm(20)
response=rnorm(20)
linear_reg <- simp_lin_R(y=response, x=predictor)
linear_reg$Coefficients
linear_reg$Fitted
linear_reg$MSE
linear_reg$Standard_Error
linear_reg$Residuals
linear_reg$`95pct_conf`
```

Thus the one can use this output to produce simple linear regression illustrations.

```{r}
plot(x=predictor, y=response)
lines(x=predictor, y=linear_reg$Fitted, col="red")
```
